\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty

### 2014-10-03 paper.tex
went over related work, changed structure

\section{Problem Definition}
Before we present the problem definition, we introduce the our grasping model, the line of action.

\subsection{Line of action}
Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

@@

\section{Evaluating a Grasp}
 In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$. We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating the expectation $E$ efficiently.

@@

\section{Future Work}
Our results are promising and they suggest many avenues of future work.
First, we are actively working to apply this approach to 3D environments.
In particular, we are interested in investigating the entire end-to-end pipeline of perception, grasp planning, and grasp execution.
Next, in principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
It can further be applied to other grasp quality metrics.
Next, we are investigating the application of recent results from reinforcement learning or bandit theory for analytic stopping criteria for the sampling.
One particular challenge is that shape uncertainty is rarely parametric leading to problems with many recent bounds and optimality conditions.

>>>>

\section{Preliminaries and Problem Definition}
Before we present the problem definition, we introduce a way to evaluate the quality of a grasp and our grasping model, the line of action.

Since we are in an uncertain environment, we are interested in calculating the expected quality, or $E(Q)$. $E(Q)$ is computed by sampling from our distributions on pose, shape or material properties (friction coefficient or density) and averaging the qualities that are computed. Reducing the time to do this for a large number of grasps is the primary focus of the paper.

\subsection{Line of action}
In an uncertain environment one wouldn't actually know the true $g$, thus we have to work with the trajectory of the gripper. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.
While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial based on. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

@@

\section{Evaluating a Grasp on Gaussian Process Implicit Surface}
 In order to solve our problem definition, we must evaluate $E(Q(\Gamma))$ for a given grasp plan $\Gamma$. We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating the expectation $E$ efficiently.

@@

\section{Future Work}
Our results are promising and they suggest many avenues of future work. The advantage of this model is that we can have uncertainty in all elements that compose a grasp: shape, pose, friction coefficient and center of mass. While at the same time not exhaustively sampling all of our potential grasp plans.

In principle, our method can be applied to other representations of shape uncertainty such as perturbations on polygonal vertices \cite{kehoe2012estimating} or splines \cite{christopoulos2007handling}.
It can further be applied to other grasp quality metrics.

Future work, will consider applying BMAB approach to grasp planners like GraspIt! \cite{miller2004graspit} to see if we can handle uncertainty and still maintain the time constraints needed for most real time applications. Also, we currently have only tested out one bandit algorithm, succesive elimination, and had very successful results. As we scale to more complicated models, we will have a large area of research to draw from and improve our method \cite{bergemann2006bandit}.
